Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2022-06-02 doc/JFLA2022/Slides/Slides.tex
small changes to JFLA slides

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{frame}
    \frametitle{Paths and accessibility}
    \begin{block}{Theorem (K. \& S., 1981) }
      % If $\beta<\alpha<\epsilon_0$, there exists $i$ and $l$ in $\mathbb{N}$ such that $ \alpha \rplus{i, i+1, i+2, \dots,l} \beta$.

          \label{fig:accessibility}
        \begin{tikzpicture}[very thick, scale=0.25]
\node (alpha) at (0,0) {$\alpha$};
    \node (beta) at (40, 0){$\beta$};

  \draw[->, very thick,black] (alpha)--  node [above]{$>$} (beta);

  \node (alpha1) at (5,5) {};
  \node (alpha2) at (13,5) {};
    \node (alpha3) at (20,5) {};
  \node (alpha4) at (25,5) {};
  \draw [->, dashed,very thick,red] (alpha)-- node [below, rotate=40]{$i$}  (alpha1);
  \draw [->, dashed,very thick,red] (alpha1)-- node [below]{$i+1$}  (alpha2);
   \draw [->, dashed,very thick,red] (alpha2)-- node [below]{$i+2$}  (alpha3);
    \draw [->, dashed,very thick,red] (alpha3)-- node [below]{$i+3$}  (alpha4);
  \node (dots) at (30,5) {$\dots$};
  \node (search) at (32,5){};
 \draw [->, dashed, very thick,red] (search)-- node [below, rotate=-26]{$l$}  (beta);
\end{tikzpicture}

%\pause
\textbf{Remark:} The proof is not trivial. The built path could miss $\beta$!

@@

\textbf{Cor:} There is no decreasing measure mapping hydras to  $[0, \mu)$ (for any $\mu<\epsilon_0$)  for proving the termination of the considered kind of hydra battles.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
  \begin{frame}
    \frametitle{Paths and accessibility}
    \begin{block}{ }
      % If $\beta<\alpha<\epsilon_0$, there exists $i$ and $l$ in $\mathbb{N}$ such that $ \alpha \rplus{i, i+1, i+2, \dots,l} \beta$.

          \label{fig:accessibility}
        \begin{tikzpicture}[very thick, scale=0.25]
\node (alpha) at (0,0) {$\alpha$};
    \node (beta) at (35, 0){\textcolor{red}{$\beta$}};
   \node (zero) at (40, 0){$0$};

  \draw[->, very thick,black] (alpha)--  node [above]{$>$} (beta);
 \draw[->, very thick,black] (beta)--  node [above]{$>$} (zero);
  \node (alpha1) at (5,5) {};
  \node (alpha2) at (13,5) {};
    \node (alpha3) at (20,5) {};
  \node (alpha4) at (25,5) {};
  \draw [->, dashed,very thick,red] (alpha)-- node [below, rotate=40]{$i$}  (alpha1);
  \draw [->, dashed,very thick,red] (alpha1)-- node [below]{$i+1$}  (alpha2);
   \draw [->, dashed,very thick,red] (alpha2)-- node [below]{$i+2$}  (alpha3);
    \draw [->, dashed,very thick,red] (alpha3)-- node [below]{$i+3$}  (alpha4);
    \only<1>{\node (dots) at (26,5) {$\;\dots\;?$};}
     \only<2>{\node (dots) at (26,5) {\textcolor{red}{$\;\dots\;$}};}
  \node (search) at (32,5){};
 \only<2>{\draw [->, dashed, very thick,red] (search)-- node [below, rotate=-26]{$l$}  (beta);}
\end{tikzpicture}

\only<2>{OK for large enough $i$ (K. \& S., 1981);}
\vspace{6pt}

%\pause
\only<2>{\textbf{Remark:} The proof is not trivial. The built path could miss $\beta$!}

@@

\only<2>{\textbf{Cor:} There is no decreasing measure mapping hydras to  $[0, \mu)$ (for any $\mu<\epsilon_0$)  for proving the termination of the considered kind of hydra battles.}
